Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
rough draft for second part of intro

    A seminal list-based scheduling heuristic for workflows is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority and (ii) the tasks are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next.
    HEFT has been extended (e.g.\ by Shi and Dongarra~\cite{SHI2006665}) and adjusted for a variety of different scheduling problem formulations. 
    Yet, none of them adheres to memory constraints -- also see our discussion of related work
    in Section~\ref{sec:related-work}. (\skug{check in related work if true!}).
        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

    \begin{itemize}
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

>>>>

    A seminal list scheduling heuristic for workflows is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority and (ii) the tasks in a priority-ordered list are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next.
    HEFT has been extended (e.g.\ by Shi and Dongarra~\cite{SHI2006665}) and adjusted for a variety of different scheduling problem formulations. 
    Yet, none of them adheres to memory constraints -- also see our discussion of related work
    in Section~\ref{sec:related-work}. (\skug{check in related work if true!}).
        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

    Another limitation in practice of HEFT (and many other scheduling strategies) is their 
    assumption that the task running times provided to them are accurate. In practice this is 
    not the case and deviations from user estimates or historical measurements are 
    very common~\cite{TODO}. As a consequence, one should adapt the schedule when \emph{major}
    deviations occur. List-based schedulers such as HEFT are, however, not designed for 
    such an adaptation~\cite{TODO}.\hmey{Svetlana, Anne: is this a fair statement?}
%    and would compute a completely new schedule from scratch.
